True versus apparent shapes of astrophysical bow shocks

### 2017-03-21 papers/Paper1/quadrics-appendix.tex
Add Herschel comparison figure and p-value test

%%% Local Variables:
%%% mode: latex
%%% TeX-master: quadrics-bowshock
%%% End:

>>>>

\section{Distribution of p-values for all correlations tested}
\label{sec:distr-p-values}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/p-value-histogram}
  \caption{Histogram of \(p\)-values for all Anderson--Darling
    non-parametric 2-sample tests performed during the analysis of
    section~\ref{sec:comp-with-observ}.  The vertical dashed line
    shows the traditional threshold value for significance:
    \(p = 0.05\). The red solid line shows the expected distribution
    of \(p\)-values that would be obtained if no significant
    correlations existed.}
  \label{fig:histo-p-values}
\end{figure}

All astronomical data analysis is \emph{post hoc} analysis, since the universe was not set up to test a particular hypothesis (as far as we know).  It is therefore important to guard against the ``multiple comparisons problem'', whereby seemingly significant correlations are found where none really exist, simply by virtue of the large number of tests that were carried out.

Under the more conservative Holm--Bonferroni method, only comparisons with \(p < 0.001\) would be significant.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "quadrics-bowshock.tex"
%%% End:

### 2017-03-21 papers/Paper1/sec-quadrics-observations.tex
Compare LL arcs with OB arcs
Add Herschel comparison figure and p-value test

@@

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{figs/annotated-ll-arcs}
  \caption[]{Stationary bow shock arcs in the Orion Nebula}
  \label{fig:ll-arcs}
\end{figure*}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/mipsgal-Rc-R90-vs-Herschel}
  \caption[]{Comparison of RSG/AGB arcs with OB star arcs.}
  \label{fig:herschel-compare-mipsgal}
\end{figure}

@@

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{figs/annotated-ll-arcs}
  \caption[]{Stationary bow shock arcs in the Orion Nebula.}
  \label{fig:ll-arcs}
\end{figure*}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/mipsgal-Rc-R90-vs-Orion}
  \caption[]{Comparison of Orion with OB stars.}
  \label{fig:ll-compare-mipsgal}
\end{figure}
